---
title: "Inferential Data Analysis"
author: "Donato Scarano"
date: "03 luglio 2018"
output:
  pdf_document: default
  html_document: default
---

Basic Inferential Data Analysis

In this project, we're going to analyze the ToothGrowth data in the R datasets package.

#Load the ToothGrowth data and perform some basic exploratory data analyses.

```{r echo=TRUE}
library(datasets)
data("ToothGrowth")
```

Let's start looking at the structure of the dataset and let us consult the help section with the dataset details.

```{r echo=TRUE}
str(ToothGrowth)
?ToothGrowth
```

We want to see first how the dose received either via Vitamin C or Orange Juice is related to the tooth length.
Let us plot the relation above to get a first look.

```{r echo=TRUE}
plot(ToothGrowth$len ~ ToothGrowth$dose, xlab = "Dose", ylab = "Length", col = c("red", "black"))
legend("topleft",c("Orange Juice", "Vitamin C"),pch = 1, col = c("red", "black"))
```
There seems to be a positive correlation between the dose and the tooth growth.

#Provide a basic summary of the data.

Let us use the summary function to obtain a basic outline

```{r echo=TRUE}
summary(ToothGrowth)
```

#Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)

Confidence intervals, we fit a linear model and we apply the confint function to obtain them:

```{r echo=TRUE}
fitd <- lm(ToothGrowth$len ~ ToothGrowth$dose)
confint(fitd)
```

Same process can be apllied for supp variable as well:

```{r echo=TRUE}
fits <- lm(ToothGrowth$len ~ ToothGrowth$supp)
confint(fits)
```

or for both togheter:

```{r echo=TRUE}
fittotal <- lm(ToothGrowth$len~ToothGrowth$supp + ToothGrowth$dose)
confint(fittotal)
```

#State your conclusions and the assumptions needed for your conclusions.

There is certainly a positive correlation between tooth length and dose but we see a negative one between tooth length and supp VC as shown in confidence interval above. OJ seems to have a greater impact than VC.